Comparative Evaluation of Spark and Flink Stream Processing

### 2017-03-03 paper/paper.tex
[paper] updated Flink's implementation of sector change detection.

 The Flink implementation of sector change detection workload, uses the \texttt{FlinkKafkaConsumer09} that read the ADS-B messages stream from Kafka, which used to construct \texttt{DataStream} instance. The \texttt{DataStream} records are parsed to tuples of aircraft ID and aircraft's position, by a configured \texttt{map} function. The irrelevant tuples are filtered based on the message type using a \texttt{filter} operation. Afterward, the tuples with common IDs are grouped together by the \texttt{keyBy} operator. Since the Flink streaming processes the stream records as it come, a defined \texttt{reduce} operator assign corresponding sector of new tuple, and the old tuple with same ID is used to retrieve the previous sector to attach it to the new tuple, while the old tuple is discarded. Finally, the tuples with different previous and current sector that represent change in sector case, they are filtered using defined \texttt{filter} transformation.
 \end{itemize}
\section{Performance Results}

>>>>

 The Flink's implementation of sector change detection workload, uses the \texttt{FlinkKafkaConsumer09} that reads the position messages (i.e., ADS-B) stream from Kafka, which used to construct \texttt{DataStream} instance. The \texttt{DataStream}'s records are mapped to tuples of (aircraft ID and aircraft's position), by a configured \texttt{map} transformation. The irrelevant tuples are filtered based on the message type using a \texttt{filter} operation. Afterward, the tuples that shares a common IDs are grouped together by the \texttt{keyBy} operator. Since the Flink streaming processes the stream records as it come, a defined \texttt{reduce} operator assign corresponding sector of position on new tuple, while the old tuple with same ID is used to retrieve the previous sector to attach it to the new tuple, while the old tuple is discarded. Finally, the tuples (i.e., tuple of (aircraft ID, position message)) with different previous and current sector are filtered using defined \texttt{filter} transformation.

 //TODO: add comparison between spark and Flink approaches 
 \end{itemize}
\section{Performance Results}
